\begin{titlepage}
	\null\vspace{\fill}
	% \input{Files/Abstract}
	\begin{abstract}
		This report is divided into parts: An Introduction to Algebra and Geometry followed by An Introduction to \Grob Bases then Applications of \Grob Bases. 
		We start with an introduction to algebraic concepts, focussing over polynomials, ideals and their algorithms. Then we study geometric concepts such as varieties and their relationship with ideals which is probed with interesting problem. One such problem of ``Ideal Membership'' is broken down into simpler cases and the development of \Grob Bases Theory and Computation is motivated using it. Then, we focus on select applications of \Grob Bases from countless many available in literature and also discuss SageMath implementations for some of them.
		I have tried to make this report interesting and also covered fundamentals.
		Still, this is just a \emph{glimpse} of an extensive topic like \Grob Bases.
		Finally, I encourage you to look at all the SageMath programs and their diverse and exciting applications \href{https://github.com/paramrathour/Groebner-Basis-Applications}{here}.
	\end{abstract}
	\vspace{\fill}
	\renewcommand{\abstractname}{Acknowledgements}
	% \input{Files/Acknowledgements}
	\begin{abstract}
		This report was developed as a part of the course \emph{EE451: Supervised Research Exposition} to compile together my learnings and experiences.
		I thank my parents for always motivating me.
		I would also like to express gratitude to my guide: Prof. Debasattam for introducing me to this fascinating topic.
		Most of the content here is inspired by \cite{book:coxlittleoshea}, many statements are directly taken from here and my explanations are based on my understanding from the book.
		And, lastly thanks to you, reader, I have worked hard in making this report, in the hope that this work helps you in some way.
	\end{abstract}
	\vspace{\fill}
\end{titlepage}